### 2020-05-15 serial_analysis.tex
done

% Created by tikzDevice version 0.12.3 on 2020-04-12 17:51:37
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}

@@

\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (578.16,289.08);
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (289.08,289.08);
\definecolor{drawColor}{RGB}{255,255,255}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (  0.00,  0.00) rectangle (289.08,289.08);
\end{scope}
\begin{scope}
\path[clip] ( 34.64, 30.69) rectangle (283.58,266.42);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 34.64, 30.69) rectangle (283.58,266.42);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 41.97,138.18) -- ( 41.97,138.18);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 41.97,138.18) -- ( 41.97,138.18);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 39.22,138.18) --
	( 39.22,138.18) --
	( 44.71,138.18) --
	( 44.71,138.18) --
	( 39.22,138.18) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] ( 39.22,138.18) -- ( 44.71,138.18);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 56.61,226.33) -- ( 56.61,234.97);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 56.61,209.04) -- ( 56.61,186.58);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 53.86,226.33) --
	( 53.86,209.04) --
	( 59.36,209.04) --
	( 59.36,226.33) --
	( 53.86,226.33) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] ( 53.86,217.69) -- ( 59.36,217.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 63.93,196.95) -- ( 63.93,228.06);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 63.93,158.92) -- ( 63.93,152.01);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 61.19,196.95) --
	( 61.19,158.92) --
	( 66.68,158.92) --
	( 66.68,196.95) --
	( 61.19,196.95) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] ( 61.19,165.84) -- ( 66.68,165.84);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 71.25,200.40) -- ( 71.25,207.32);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 71.25,186.58) -- ( 71.25,179.66);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 68.51,200.40) --
	( 68.51,186.58) --
	( 74.00,186.58) --
	( 74.00,200.40) --
	( 68.51,200.40) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] ( 68.51,193.49) -- ( 74.00,193.49);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 78.57,221.14) -- ( 78.57,234.97);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 78.57,172.75) -- ( 78.57,138.18);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 75.83,221.14) --
	( 75.83,172.75) --
	( 81.32,172.75) --
	( 81.32,221.14) --
	( 75.83,221.14) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] ( 75.83,207.32) -- ( 81.32,207.32);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 85.90,221.14) -- ( 85.90,221.14);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 85.90,221.14) -- ( 85.90,221.14);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 83.15,221.14) --
	( 83.15,221.14) --
	( 88.64,221.14) --
	( 88.64,221.14) --
	( 83.15,221.14) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] ( 83.15,221.14) -- ( 88.64,221.14);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 93.22,238.42) -- ( 93.22,255.71);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 93.22,203.86) -- ( 93.22,186.58);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 90.47,238.42) --
	( 90.47,203.86) --
	( 95.96,203.86) --
	( 95.96,238.42) --
	( 90.47,238.42) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] ( 90.47,221.14) -- ( 95.96,221.14);

\path[draw=drawColor,line width= 0.6pt,line join=round] (100.54,200.40) -- (100.54,207.32);

\path[draw=drawColor,line width= 0.6pt,line join=round] (100.54,186.58) -- (100.54,179.66);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 97.79,200.40) --
	( 97.79,186.58) --
	(103.29,186.58) --
	(103.29,200.40) --
	( 97.79,200.40) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] ( 97.79,193.49) -- (103.29,193.49);

\path[draw=drawColor,line width= 0.6pt,line join=round] (107.86,214.23) -- (107.86,214.23);

\path[draw=drawColor,line width= 0.6pt,line join=round] (107.86,214.23) -- (107.86,214.23);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (105.12,214.23) --
	(105.12,214.23) --
	(110.61,214.23) --
	(110.61,214.23) --
	(105.12,214.23) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (105.12,214.23) -- (110.61,214.23);

\path[draw=drawColor,line width= 0.6pt,line join=round] (115.18,198.67) -- (115.18,214.23);

\path[draw=drawColor,line width= 0.6pt,line join=round] (115.18,164.11) -- (115.18,158.92);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (112.44,198.67) --
	(112.44,164.11) --
	(117.93,164.11) --
	(117.93,198.67) --
	(112.44,198.67) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (112.44,179.66) -- (117.93,179.66);

\path[draw=drawColor,line width= 0.6pt,line join=round] (122.50,186.58) -- (122.50,234.97);

\path[draw=drawColor,line width= 0.6pt,line join=round] (122.50,138.18) -- (122.50,103.62);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (119.76,186.58) --
	(119.76,138.18) --
	(125.25,138.18) --
	(125.25,186.58) --
	(119.76,186.58) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (119.76,158.92) -- (125.25,158.92);
\definecolor{fillColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (129.83,221.14) circle (  1.96);

\path[draw=drawColor,line width= 0.6pt,line join=round] (129.83,171.02) -- (129.83,193.49);

\path[draw=drawColor,line width= 0.6pt,line join=round] (129.83,139.91) -- (129.83,124.36);
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (127.08,171.02) --
	(127.08,139.91) --
	(132.57,139.91) --
	(132.57,171.02) --
	(127.08,171.02) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (127.08,155.47) -- (132.57,155.47);

\path[draw=drawColor,line width= 0.6pt,line join=round] (137.15,183.12) -- (137.15,200.40);

\path[draw=drawColor,line width= 0.6pt,line join=round] (137.15,148.55) -- (137.15,117.45);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (134.40,183.12) --
	(134.40,148.55) --
	(139.89,148.55) --
	(139.89,183.12) --
	(134.40,183.12) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (134.40,165.84) -- (139.89,165.84);

\path[draw=drawColor,line width= 0.6pt,line join=round] (144.47,172.75) -- (144.47,214.23);

\path[draw=drawColor,line width= 0.6pt,line join=round] (144.47,131.27) -- (144.47,110.53);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (141.72,172.75) --
	(141.72,131.27) --
	(147.21,131.27) --
	(147.21,172.75) --
	(141.72,172.75) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (141.72,152.01) -- (147.21,152.01);

\path[draw=drawColor,line width= 0.6pt,line join=round] (151.79,179.66) -- (151.79,221.14);

\path[draw=drawColor,line width= 0.6pt,line join=round] (151.79,138.18) -- (151.79,117.45);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (149.05,179.66) --
	(149.05,138.18) --
	(154.54,138.18) --
	(154.54,179.66) --
	(149.05,179.66) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (149.05,158.92) -- (154.54,158.92);

\path[draw=drawColor,line width= 0.6pt,line join=round] (159.11,184.85) -- (159.11,228.06);

\path[draw=drawColor,line width= 0.6pt,line join=round] (159.11,126.09) -- (159.11, 55.23);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (156.37,184.85) --
	(156.37,126.09) --
	(161.86,126.09) --
	(161.86,184.85) --
	(156.37,184.85) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (156.37,155.47) -- (161.86,155.47);

\path[draw=drawColor,line width= 0.6pt,line join=round] (166.43,174.48) -- (166.43,200.40);

\path[draw=drawColor,line width= 0.6pt,line join=round] (166.43,129.54) -- (166.43,110.53);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (163.69,174.48) --
	(163.69,129.54) --
	(169.18,129.54) --
	(169.18,174.48) --
	(163.69,174.48) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (163.69,152.01) -- (169.18,152.01);

\path[draw=drawColor,line width= 0.6pt,line join=round] (173.76,171.02) -- (173.76,193.49);

\path[draw=drawColor,line width= 0.6pt,line join=round] (173.76,133.00) -- (173.76,117.45);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (171.01,171.02) --
	(171.01,133.00) --
	(176.50,133.00) --
	(176.50,171.02) --
	(171.01,171.02) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (171.01,152.01) -- (176.50,152.01);

\path[draw=drawColor,line width= 0.6pt,line join=round] (181.08,152.01) -- (181.08,179.66);

\path[draw=drawColor,line width= 0.6pt,line join=round] (181.08,110.53) -- (181.08, 82.88);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (178.33,152.01) --
	(178.33,110.53) --
	(183.82,110.53) --
	(183.82,152.01) --
	(178.33,152.01) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (178.33,131.27) -- (183.82,131.27);

\path[draw=drawColor,line width= 0.6pt,line join=round] (188.40,165.84) -- (188.40,193.49);

\path[draw=drawColor,line width= 0.6pt,line join=round] (188.40,110.53) -- (188.40, 75.97);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (185.65,165.84) --
	(185.65,110.53) --
	(191.14,110.53) --
	(191.14,165.84) --
	(185.65,165.84) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (185.65,138.18) -- (191.14,138.18);

\path[draw=drawColor,line width= 0.6pt,line join=round] (195.72,160.65) -- (195.72,200.40);

\path[draw=drawColor,line width= 0.6pt,line join=round] (195.72,108.80) -- (195.72, 82.88);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (192.97,160.65) --
	(192.97,108.80) --
	(198.47,108.80) --
	(198.47,160.65) --
	(192.97,160.65) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (192.97,134.73) -- (198.47,134.73);
\definecolor{fillColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (203.04, 48.31) circle (  1.96);

\path[draw=drawColor,line width= 0.6pt,line join=round] (203.04,155.47) -- (203.04,179.66);

\path[draw=drawColor,line width= 0.6pt,line join=round] (203.04,120.90) -- (203.04,103.62);
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (200.30,155.47) --
	(200.30,120.90) --
	(205.79,120.90) --
	(205.79,155.47) --
	(200.30,155.47) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (200.30,138.18) -- (205.79,138.18);

\path[draw=drawColor,line width= 0.6pt,line join=round] (210.36,143.37) -- (210.36,172.75);

\path[draw=drawColor,line width= 0.6pt,line join=round] (210.36,107.08) -- (210.36, 62.14);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (207.62,143.37) --
	(207.62,107.08) --
	(213.11,107.08) --
	(213.11,143.37) --
	(207.62,143.37) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (207.62,127.81) -- (213.11,127.81);

\path[draw=drawColor,line width= 0.6pt,line join=round] (217.69,131.27) -- (217.69,145.10);

\path[draw=drawColor,line width= 0.6pt,line join=round] (217.69, 96.71) -- (217.69, 75.97);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (214.94,131.27) --
	(214.94, 96.71) --
	(220.43, 96.71) --
	(220.43,131.27) --
	(214.94,131.27) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (214.94,117.45) -- (220.43,117.45);

\path[draw=drawColor,line width= 0.6pt,line join=round] (225.01,134.73) -- (225.01,145.10);

\path[draw=drawColor,line width= 0.6pt,line join=round] (225.01,113.99) -- (225.01, 82.88);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (222.26,134.73) --
	(222.26,113.99) --
	(227.75,113.99) --
	(227.75,134.73) --
	(222.26,134.73) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (222.26,124.36) -- (227.75,124.36);

\path[draw=drawColor,line width= 0.6pt,line join=round] (232.33,134.73) -- (232.33,145.10);

\path[draw=drawColor,line width= 0.6pt,line join=round] (232.33,113.99) -- (232.33, 96.71);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (229.58,134.73) --
	(229.58,113.99) --
	(235.07,113.99) --
	(235.07,134.73) --
	(229.58,134.73) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (229.58,124.36) -- (235.07,124.36);

\path[draw=drawColor,line width= 0.6pt,line join=round] (239.65,126.09) -- (239.65,131.27);

\path[draw=drawColor,line width= 0.6pt,line join=round] (239.65,115.72) -- (239.65,110.53);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (236.90,126.09) --
	(236.90,115.72) --
	(242.40,115.72) --
	(242.40,126.09) --
	(236.90,126.09) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (236.90,120.90) -- (242.40,120.90);

\path[draw=drawColor,line width= 0.6pt,line join=round] (246.97,110.53) -- (246.97,110.53);

>>>>

% Created by tikzDevice version 0.12.3 on 2020-05-14 21:20:58
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}

@@

\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (867.24,289.08);
\begin{scope}
\path[clip] ( 10.17,  0.00) rectangle (278.91,289.08);
\definecolor{drawColor}{RGB}{255,255,255}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 10.17,  0.00) rectangle (278.91,289.08);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (867.24,289.08);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 44.82, 30.69) rectangle (273.41,266.42);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,rotate=-45.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (206.43,192.30) {maximum observable};

\node[text=drawColor,rotate=-45.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at ( 92.13, 70.86) {minimum observable};

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (130.54,266.42) --
	(137.68,259.28) --
	(144.83,252.14) --
	(151.97,244.99) --
	(159.11,237.85) --
	(166.26,230.71) --
	(173.40,223.56) --
	(180.54,216.42) --
	(187.69,209.27) --
	(194.83,202.13) --
	(201.97,194.99) --
	(209.12,187.84) --
	(216.26,180.70) --
	(223.40,173.56) --
	(230.55,166.41) --
	(237.69,159.27) --
	(244.83,152.13) --
	(251.98,144.98) --
	(259.12,137.84) --
	(266.27,130.70) --
	(273.41,123.55);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] ( 44.82,116.41) --
	( 51.96,109.26) --
	( 59.10,102.12) --
	( 66.25, 94.98) --
	( 73.39, 87.83) --
	( 80.53, 80.69) --
	( 87.68, 73.55) --
	( 94.82, 66.40) --
	(101.96, 59.26) --
	(109.11, 52.12) --
	(116.25, 44.97) --
	(123.39, 37.83) --
	(130.54, 30.69);
\definecolor{fillColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 44.82,137.84) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 59.10,219.10) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 66.25,183.08) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 73.39,194.99) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 80.53,194.99) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 87.68,223.56) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 94.82,223.56) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (101.96,194.99) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (109.11,216.42) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (116.25,184.27) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (123.39,159.58) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (130.54,159.72) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (137.68,165.29) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (144.83,150.04) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (151.97,160.95) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (159.11,149.30) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (166.26,144.74) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (173.40,149.93) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (180.54,133.26) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (187.69,138.29) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (194.83,129.96) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (201.97,127.28) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (209.12,127.33) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (216.26,119.77) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (223.40,115.57) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (230.55,124.85) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (237.69,122.12) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (244.83,109.26) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (259.12, 87.83) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (273.41, 73.55) circle (  1.96);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 44.82,137.84) --
	( 44.82,137.84);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 44.82,137.84) --
	( 44.82,137.84);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 44.82,137.84) --
	( 44.82,137.84);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 59.10,236.60) --
	( 59.10,236.60);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 59.10,236.60) --
	( 59.10,191.59);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 59.10,191.59) --
	( 59.10,191.59);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 66.25,227.49) --
	( 66.25,227.49);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 66.25,227.49) --
	( 66.25,152.84);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 66.25,152.84) --
	( 66.25,152.84);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 73.39,208.56) --
	( 73.39,208.56);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 73.39,208.56) --
	( 73.39,181.41);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 73.39,181.41) --
	( 73.39,181.41);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 80.53,236.42) --
	( 80.53,236.42);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 80.53,236.42) --
	( 80.53,141.41);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 80.53,141.41) --
	( 80.53,141.41);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 87.68,223.56) --
	( 87.68,223.56);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 87.68,223.56) --
	( 87.68,223.56);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 87.68,223.56) --
	( 87.68,223.56);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 94.82,257.49) --
	( 94.82,257.49);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 94.82,257.49) --
	( 94.82,189.63);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 94.82,189.63) --
	( 94.82,189.63);

\path[draw=drawColor,line width= 0.6pt,line join=round] (101.96,208.56) --
	(101.96,208.56);

\path[draw=drawColor,line width= 0.6pt,line join=round] (101.96,208.56) --
	(101.96,181.41);

\path[draw=drawColor,line width= 0.6pt,line join=round] (101.96,181.41) --
	(101.96,181.41);

\path[draw=drawColor,line width= 0.6pt,line join=round] (109.11,216.42) --
	(109.11,216.42);

\path[draw=drawColor,line width= 0.6pt,line join=round] (109.11,216.42) --
	(109.11,216.42);

\path[draw=drawColor,line width= 0.6pt,line join=round] (109.11,216.42) --
	(109.11,216.42);

\path[draw=drawColor,line width= 0.6pt,line join=round] (116.25,214.81) --
	(116.25,214.81);

\path[draw=drawColor,line width= 0.6pt,line join=round] (116.25,214.81) --
	(116.25,159.81);

\path[draw=drawColor,line width= 0.6pt,line join=round] (116.25,159.81) --
	(116.25,159.81);

\path[draw=drawColor,line width= 0.6pt,line join=round] (123.39,229.99) --
	(123.39,229.99);

\path[draw=drawColor,line width= 0.6pt,line join=round] (123.39,229.99) --
	(123.39,109.98);

\path[draw=drawColor,line width= 0.6pt,line join=round] (123.39,109.98) --
	(123.39,109.98);

\path[draw=drawColor,line width= 0.6pt,line join=round] (130.54,212.85) --
	(130.54,212.85);

\path[draw=drawColor,line width= 0.6pt,line join=round] (130.54,212.85) --
	(130.54,126.23);

\path[draw=drawColor,line width= 0.6pt,line join=round] (130.54,126.23) --
	(130.54,126.23);

\path[draw=drawColor,line width= 0.6pt,line join=round] (137.68,198.92) --
	(137.68,198.92);

\path[draw=drawColor,line width= 0.6pt,line join=round] (137.68,198.92) --
	(137.68,122.84);

\path[draw=drawColor,line width= 0.6pt,line join=round] (137.68,122.84) --
	(137.68,122.84);

\path[draw=drawColor,line width= 0.6pt,line join=round] (144.83,212.31) --
	(144.83,212.31);

\path[draw=drawColor,line width= 0.6pt,line join=round] (144.83,212.31) --
	(144.83,109.26);

\path[draw=drawColor,line width= 0.6pt,line join=round] (144.83,109.26) --
	(144.83,109.26);

\path[draw=drawColor,line width= 0.6pt,line join=round] (151.97,223.56) --
	(151.97,223.56);

\path[draw=drawColor,line width= 0.6pt,line join=round] (151.97,223.56) --
	(151.97,122.30);

\path[draw=drawColor,line width= 0.6pt,line join=round] (151.97,122.30) --
	(151.97,122.30);

\path[draw=drawColor,line width= 0.6pt,line join=round] (159.11,222.31) --
	(159.11,222.31);

\path[draw=drawColor,line width= 0.6pt,line join=round] (159.11,222.31) --
	(159.11, 91.58);

\path[draw=drawColor,line width= 0.6pt,line join=round] (159.11, 91.58) --
	(159.11, 91.58);

\path[draw=drawColor,line width= 0.6pt,line join=round] (166.26,191.77) --
	(166.26,191.77);

\path[draw=drawColor,line width= 0.6pt,line join=round] (166.26,191.77) --
	(166.26,109.26);

\path[draw=drawColor,line width= 0.6pt,line join=round] (166.26,109.26) --
	(166.26,109.26);

\path[draw=drawColor,line width= 0.6pt,line join=round] (173.40,190.52) --
	(173.40,190.52);

\path[draw=drawColor,line width= 0.6pt,line join=round] (173.40,190.52) --
	(173.40,116.41);

\path[draw=drawColor,line width= 0.6pt,line join=round] (173.40,116.41) --
	(173.40,116.41);

\path[draw=drawColor,line width= 0.6pt,line join=round] (180.54,167.13) --
	(180.54,167.13);

\path[draw=drawColor,line width= 0.6pt,line join=round] (180.54,167.13) --
	(180.54, 87.48);

\path[draw=drawColor,line width= 0.6pt,line join=round] (180.54, 87.48) --
	(180.54, 87.48);

\path[draw=drawColor,line width= 0.6pt,line join=round] (187.69,193.74) --
	(187.69,193.74);

\path[draw=drawColor,line width= 0.6pt,line join=round] (187.69,193.74) --
	(187.69, 80.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] (187.69, 80.69) --
	(187.69, 80.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] (194.83,181.77) --
	(194.83,181.77);

\path[draw=drawColor,line width= 0.6pt,line join=round] (194.83,181.77) --
	(194.83, 87.48);

\path[draw=drawColor,line width= 0.6pt,line join=round] (194.83, 87.48) --
	(194.83, 87.48);

\path[draw=drawColor,line width= 0.6pt,line join=round] (201.97,172.84) --
	(201.97,172.84);

\path[draw=drawColor,line width= 0.6pt,line join=round] (201.97,172.84) --
	(201.97, 44.97);

\path[draw=drawColor,line width= 0.6pt,line join=round] (201.97, 44.97) --
	(201.97, 44.97);

\path[draw=drawColor,line width= 0.6pt,line join=round] (209.12,167.84) --
	(209.12,167.84);

\path[draw=drawColor,line width= 0.6pt,line join=round] (209.12,167.84) --
	(209.12, 70.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] (209.12, 70.69) --
	(209.12, 70.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] (216.26,144.98) --
	(216.26,144.98);

\path[draw=drawColor,line width= 0.6pt,line join=round] (216.26,144.98) --
	(216.26, 79.26);

\path[draw=drawColor,line width= 0.6pt,line join=round] (216.26, 79.26) --
	(216.26, 79.26);

\path[draw=drawColor,line width= 0.6pt,line join=round] (223.40,142.13) --
	(223.40,142.13);

\path[draw=drawColor,line width= 0.6pt,line join=round] (223.40,142.13) --
	(223.40, 92.12);

\path[draw=drawColor,line width= 0.6pt,line join=round] (223.40, 92.12) --
	(223.40, 92.12);

\path[draw=drawColor,line width= 0.6pt,line join=round] (230.55,144.98) --
	(230.55,144.98);

\path[draw=drawColor,line width= 0.6pt,line join=round] (230.55,144.98) --
	(230.55, 98.55);

\path[draw=drawColor,line width= 0.6pt,line join=round] (230.55, 98.55) --
	(230.55, 98.55);

\path[draw=drawColor,line width= 0.6pt,line join=round] (237.69,130.70) --
	(237.69,130.70);

\path[draw=drawColor,line width= 0.6pt,line join=round] (237.69,130.70) --
	(237.69,109.98);

\path[draw=drawColor,line width= 0.6pt,line join=round] (237.69,109.98) --
	(237.69,109.98);

\path[draw=drawColor,line width= 0.6pt,line join=round] (244.83,109.26) --
	(244.83,109.26);

\path[draw=drawColor,line width= 0.6pt,line join=round] (244.83,109.26) --
	(244.83,109.26);

\path[draw=drawColor,line width= 0.6pt,line join=round] (244.83,109.26) --
	(244.83,109.26);

\path[draw=drawColor,line width= 0.6pt,line join=round] (259.12, 87.83) --
	(259.12, 87.83);

\path[draw=drawColor,line width= 0.6pt,line join=round] (259.12, 87.83) --
	(259.12, 87.83);

\path[draw=drawColor,line width= 0.6pt,line join=round] (259.12, 87.83) --
	(259.12, 87.83);

\path[draw=drawColor,line width= 0.6pt,line join=round] (273.41,107.48) --
	(273.41,107.48);

\path[draw=drawColor,line width= 0.6pt,line join=round] (273.41,107.48) --
	(273.41, 39.62);

\path[draw=drawColor,line width= 0.6pt,line join=round] (273.41, 39.62) --
	(273.41, 39.62);
